### 2022-02-18 pre/pre.tex
inf rules

The term order is lifted to literals and clauses using the multiset extension of
$\succ$. The order is extended to multisets as follows
\cite[Sect.~2.5]{bg-01-resolution}. We write $S_1 \succ S_2$ if $S_1 \not= S_2$
and whenever $S_2(x) > S_1(x)$ then there is some $y \succ x$ such that $S_1(y)
> S_2(y)$. We use notation $S(x)$ to denote the number of occurrences of $x$ in
$S$.

@@

@@

\subsection{Inference Rules}
\subsection{The Redundancy Criterion and Simplification Rules}
\subsection{The Saturation Procedure}

>>>>

The term order is lifted to literals and clauses using the multiset extension of
$\succ$. The order is extended to multisets as follows
\cite[Sect.~2.5]{bg-01-resolution}. We write $S_1 \succ S_2$ if $S_1 \not= S_2$
and whenever $S_2(x) > S_1(x)$ then there is some $y \succ x$ such that $S_1(y)
> S_2(y)$. We use notation $S(x)$ to denote the number of occurrences of $x$ in
$S$. To use multiset extension, positive literals are represented as $ \{ \{s\},
\{t\} \}$ and negative ones as $\{ \{ s, t \} \}$. Clauses are then represented as 
multisets of such literals.

@@

\newcommand{\selfun}{\ensuremath{\mathit{Sel}}}
Literal selection function is a function that selects a (multi)subset of literals.
Superposition requires that at least one of the selected literals is negative.

@@

\subsection{Inference Rules}
\newcommand{\mgu}{\ensuremath{\mathit{mgu}}}

Before we spell out the inference rules of standard, first-order superposition
let us introduce some helpful notation, following Schulz \cite{ss-02-brainiac}.
With $t|_p$ we denote subterm of $t$ at position $p$ and with $t[p \rightarrow
t']$ replacement of this subterm with $t'$. Let \selfun be a selection function
and $\succ$ a reduction ordering, $C = l \llor C'$ a clause, and $\sigma$ a
substitution. We say that \sigmacl{l} is eligible for resolution if: (1) nothing
is selected by \selfun and \sigmacl{l} is $\succ$-maximal within literals in
\sigmacl{C} or (2) \selfun selected some literals and \sigmacl{l} is the maximal
within either positive or negative selected literals. We say \sigmacl{l} is
eligible for paramodulation if it is positive, nothing is selected and
\sigmacl{l} is the maximal literal within the literals of \sigmacl{C}.
With $\mgu(s,t)$ we denote the most general unifier of $s$ and $t$.
Using
horizontal line to separate premises and the conclusion, four inference rules of superposition are as
follows:

\[
\namedinference{ER}{s \noteq t \llor C}{\sigmacl{C}}
\]
where $\sigma = \mgu(s,t)$, and $(s \noteq t)\sigma$ is eligible
for resolution; \infname{ER} stands for equality resolution
\medskip

\[
\namedinference{EF}{s \eq t \llor u \eq v \llor C}{\sigmacl{(t \noteq v \llor u \eq v \llor C)}}
\]
where $\sigma = \mgu(u,v), \sigma(t) \not\succ \sigma(s)$ and 
$(s \eq t)\sigma$ is eligible for paramodulation; \infname{EF} stands for equality factoring
\medskip

\[
\namedinference{SP}{s \eq t \llor C \qquad u \eq v \llor D}{(u[p \leftarrow t] \eq v \llor C \llor D)\sigma}
\]
where $\sigma = \mgu(u|_p, s), \sigma(t) \not\succ \sigma(s), \sigma(v) \not\succ \sigma(u)$,
$(s \eq t)\sigma$ is eligible for paramodulation, just like $(u \eq v)\sigma$ and $u|_p$ is not a variable;
\infname{SP} stands for positive superposition 
\medskip

\[
\namedinference{SN}{s \eq t \llor C \qquad u \noteq v \llor D}{(u[p \leftarrow t] \noteq v \llor C \llor D)\sigma}
\]
where $\sigma = \mgu(u|_p, s), \sigma(t) \not\succ \sigma(s), \sigma(v) \not\succ \sigma(u)$,
$(s \eq t)\sigma$ is eligible for paramodulation, $(u \eq v)\sigma$ is eligible for resolution, and $u|_p$ is not a variable;
\infname{SN} stands for negative superposition
\medskip

\subsection{The Redundancy Criterion and Simplification Rules}

\subsection{The Saturation Procedure}
